---
title       : Project Shiny Application and Reproducible Pitch
subtitle    : shiny application
author      : Sandra Rairan
job         : R Hacker
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github:
        user: sandrarairan
        repo: mypresentation
---

## About Shiny Application

> 1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
> 2. Deploy the application on Rstudio's shiny server
> 3. Share the application link by pasting it into the provided text box
> 4. Share your server.R and ui.R code on github

--- .class #id 

## How to use the application

The application is running on:
www.rstudio.com

1. Selector for choosing dataset and Numeric entry for number of observation to view
2. Select tabPanel View
3. Select tabPanel View and return the requested dataset, declaring datasetInput as a reactive expression
4. Select tabPanel Str, information about dataset

---

## str Dataset Cars

```{r echo=FALSE,message=FALSE}
str(cars)
```

---

## str Dataset pressure

```{r echo=FALSE,message=FALSE}
str(pressure)
```






